Theoretical prediction of disrupted Min oscillation in flattened \emph{Escherichia coli}

### 2015-01-14 paper/plos.tex
a few minor edits with Jeff Tested everything on bennet.

\fixme{THE FOLLOWING NEEDS much CHANGING.  Many reaction-diffusion
  models have been proposed... There are several newer models that
  incorporate new experimental results.}
%
A number of models of the MinD protein system have been developed that
accurately describe its basic oscillatory nature.
%
Early models involved free proteins that affect each others' rates of
diffusion and membrane attachment, but do not combine into compound
states~\cite{meinhardt2001pattern}.  In 2003 Huang improved upon this
approach with a simple and very successful simulation model based on
MinD-MinE combination, ATPase hydrolysis, and MinD membrane attachment
that exhibits accurate MinD oscillations in cylindrical
cells~\cite{huang2003dynamic}. In this model cytoplasmic MinD is
recruited to the membrane by MinD that is already clustered there
(following observed non-linear attachment of MinD on the cell
membrane~\cite{hu2002dynamic,shih2002division}), and is stationary
once attached.
%
Some of these models
\cite{fange2006noise,bonny2013membrane,halatek2012highly} modify the
Huang model cited above to more accurately treat experimental findings
published after his 2003 paper \cite{Meacci2007,Loose2011}. They
introduce diffusion along the membrane that is two to three orders of
magnitude lower than that within the cytoplasm, revise the process of
MinD recruitment to the membrane, and change some of the constants
used in the model. The Bonny 2013 model assumes an instantaneous
nucleotide exchange rate at one point in the reaction cycle, and
relies upon MinE’s ability to independently remain attached to the
membrane in a manner that allows it to react with a number of MinD
proteins before disassociating.
%

@@

%% biology~\cite{lawson2013spatial, robb2014stochastic,
%%   oguz2014stochastic, fu2013deterministic, rudiger2014stochastic}, and
In this paper we use Huang's 2003 model~\cite{huang2003dynamic} in
both deterministic and stochastic variants to study flattened cells
similar to those observed by Mannik \emph{et
  al.}~\cite{mannik2009bacterial}.  \fixme{Some weak
  justification... it has been widely used.}

>>>>

A number of models of the MinD protein system have been developed that
accurately describe its basic oscillatory nature.
%
Early models involved free proteins that affect each others' rates of
diffusion and membrane attachment, but do not combine into compound
states~\cite{meinhardt2001pattern}.  In 2003 Huang improved upon this
approach with a simple and very successful simulation model based on
MinD-MinE combination, ATPase hydrolysis, and MinD membrane attachment
that exhibits accurate MinD oscillations in cylindrical
cells~\cite{huang2003dynamic}. In this model cytoplasmic MinD is
recruited to the membrane by MinD that is already clustered there
(following observed non-linear attachment of MinD on the cell
membrane~\cite{hu2002dynamic,shih2002division}), and is stationary
once attached.
%
Several models
\cite{fange2006noise,bonny2013membrane,halatek2012highly} modify
Huang's original model to more accurately treat experimental findings
published after his 2003 paper \cite{Meacci2007,Loose2011}. These
models introduce slow diffusion along the membrane (two to three
orders of magnitude slower than that within the cytoplasm), revise the
process of MinD recruitment to the membrane, and change some of the
constants used in the model. The Bonny 2013 model assumes an
instantaneous nucleotide exchange rate, and allows MinE to remain
independently attached to the membrane after dissasociating with
MinD~\cite{bonny2013membrane}.
%

@@

%% biology~\cite{lawson2013spatial, robb2014stochastic,
%%   oguz2014stochastic, fu2013deterministic, rudiger2014stochastic}, and
In this paper we use Huang's original 2003
model~\cite{huang2003dynamic}, which has been widely
used~\cite{hattne2005stochastic} \fixme{search for more}, in both
deterministic and stochastic variants to study flattened cells similar
to those observed by Mannik \emph{et al.}~\cite{mannik2009bacterial}.
\fixme{Some weak justification... it has been widely used.}
